\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale \versionline{4}

### 2015-09-10 ICRA2016/bandits_docs/includes/abstract.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\begin{abstract}
\TODO{Fill in after rest of paper done.}
\end{abstract}

>>>>

\begin{abstract}
%\TODO{Adapted from flyer, probably needs to be toned down}
Recent advances in distributed computing and machine learning combined with very large datasets of images and human speech have produced a series of results that surpass decades of research in analytic methods and, in some cases, human ability.
%For example, deep neural networks can now learn to play video games, recognize faces, and translate between languages.
This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
%We show that using using a large dataset of 3D models can speed up significantly the computation of valid grasps. 
%We develop a Multi-Armed Bandit model with correlated rewards to accelerate robust grasp planning by learning from a large dataset of prior grasps and 3D object models, and implement our algorithm on Google Compute Engine.
We show that learning from a large dataset of prior grasps and 3D object models can reduce the number of samples needed for robust grasp planning using our novel Multi-Armed Bandit algorithm with correlated rewards.
To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 unique 3D object models selected to reflect objects encountered in warehousing and the home such as tools, tableware, and toys.
Each object is labelled with up to 250 parallel-jaw grasps and the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between 3D objects and we apply it to indexing similar objects for grasp planning at scale.
%To the best of our knowledge, this dataset is the largest to-date used for grasping research.
We implement our algorithm and store our database using the Google Cloud Platform.
Experiments on a set of N test objects suggest that the time taken to plan a robust grasp is approximately $2\times$ faster on average and up to $10\times$ faster on select objects when using Dex-Net as a prior... \TODO{Update numbers}
Experiments on sensitivity indicate that....\TODO{Results of this}
Code, data, and additional information can be found at: \TODO{Url}
\end{abstract}

### 2015-09-10 ICRA2016/bandits_docs/includes/algorithm.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\section{Algorithm}

\TODO{Brief section on the high-level algorithm using the model: grasp sampling, evaluation of grasps, thompson sampling}

>>>>

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
Our algorithm, detailed in Algorithm~\ref{alg:full}, plans a sequence of grasps with high $P_F$ for a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards and priors from the grasp and 3D object data in Dex-Net.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting the next grasp to sample using Thompson sampling~\cite{laskey2015bandits}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the probability of force closure for each grasp.
Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimated of the grasp with the heighest estimated $P_F$.

\begin{algorithm}
{\small
    \SetAlgoLined
    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Samples $N_s$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Object Feature Map $\psi$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
    \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}

    \tcp{Generate candidate grasps and priors}
	$\Gamma$ = AntipodalGraspSample($\mO, N_g$) \;
	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
	\For{$\bg_k \in \Gamma$}{
		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD, N_n, \psi$)\; 
		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
	}

	\tcp{Run MAB to Evaluate Grasps}
	\For{$t = 1, .., T$}{
		$j = $ ThompsonSample($\mA_{t-1}, \mB_{t-1}$)\;
		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
		$F_{j} = $ EvaluateForceClosure($\bg_j, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, F_j, \Gamma$)\; 
		$\bg_{t}^* = $MaxLowerConfidence($\mA_{t}, \mB_{t}, p$)\;
	}
	return $\bg_T^*$\;
    \caption{Robust Grasp Planning With Multi-Armed Bandits Using Dex-Net 1.0}
    \label{alg:full}
}
\end{algorithm}

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
We use Continuous Correlated Beta Processes (CCBPs) to model correlations between the $P_F$ between grasps on different objects to utilize prior grasp and object data from Dex-Net 1.0.
CCBPS were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar.

Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as an occurence of force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ on object $\mO$ from samples of object pose, gripper pose, and friction, as described in \secref{quality}.
Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

\vspace{-2ex}
\begin{align*}
	\betadist(\alpha, \beta) = \frac{1}{B(\alpha, \beta)} \theta_k^{\alpha-1} (1 - \theta_k)^{\beta-1}
\end{align*}

A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
We measure similarity as a function of the euclidean distance between the output of a set of $N_f$ feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$, where $d_m$ is the dimension of the feature space.
Details on our feature maps are given in \secref{features} below.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.

We form a belief distribution for each candidate grasp in $\Gamma$ based on its its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
%\vspace{-2ex}
\begin{align}
	%p \left(\theta_{j} | \mD \right) &= \betadist\left( \alpha_{j,0}, \beta_{j,0} \right) \notag \\
	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g} k(\mY_{j}, \mY_{i, k}) S_{i,k} \label{eq:alpha-prior} \\
	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g}  k(\mY_{j}, \mY_{i,k}) (N_s - S_{i,k}) \label{eq:beta-prior}
\end{align}
\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled for evaluate $P_F$.
In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree descirbed in \secref{object-similarity}.
Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}
\end{align}

\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.

\subsection{Feature Representation}
\seclabel{features}
\TODO{Move elsewhere / condense? Its a lot of information coming out of nowhere}
We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.

\subsubsection{Grasp Parameters}
\seclabel{param-features}
Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx$ is the grasp center, $\bv$ is the grasp approach, and $\rho_i$ is the $i$-th moment arms.
The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).

\subsubsection{Local Surface Heightmaps}
\seclabel{heightmaps}
We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging} to capture local surface geometry.
Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
Then we assign the heightmap value
\begin{align*}
	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + s_i \bv \right) = 0
\end{align*}
\noindent where $s_1 = -1$, $s_2 = 1$, and $f$ is the SDF of object $\mO$. 
We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients to form local surface normal maps $\bd_{i,x}$ and $\bd_{i,y}$.
Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.35]{figures/illustrations/local_feature_model.png}
\caption{Three local surface heightmaps extracted on a teapot. Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.  We extract the gradients of these heightmaps as features in our robust grasp planning algorithm.}
\figlabel{local-feature-model}
\vspace*{-15pt}
\end{figure}

\subsubsection{Global Object Similarity}
\seclabel{global-sim}
While force closure is based on local surface properties of an object around contact points, measuring global similarity may be similarity may be useful because the heightmaps may not capture all possible contact points for a grasp under perturbations in object and gripper pose.
Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.

%\subsection{Thompson Sampling}
%\seclabel{thompson}
%
%Following Laskey et al.~\cite{laskey2015bandits}, we use Thompson sampling to select the next grasp to evaluate given belief distributions on the $P_F$ for each grasp on iteration $t$ specified by estimates $\mA_t = \{\alpha_{1,t}, ..., \alpha_{K,t}\}$ and $\mB_t = \{\beta_{1,t}, ..., \beta_{K,t}\}$.
%Thompson sampling samples a probability of force closure $\hat{\theta}_{j,t} \sim B(\alpha_{j,t}, \beta_{j,t})$ for all grasps $j = 1, ..., K$, then selects the grasp $j_t^* = \myargmax{j} \hat{\theta}_{j,t}$ to evaluate next.
%Several other criteria exist for selecting the next evaluation in MAB, such as Gittins indices~\cite{laskey2015bandits}, Upper Confidence Bounds~\cite{boularias2015learning}, and Expected Improvement~\cite{montesano2012active}.

### 2015-09-10 ICRA2016/bandits_docs/includes/background.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.22]{figures/illustrations/correlated_bandits.png}
\caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle. (Top Right) The true probability of force closure $P_F$ as a function of the angle of the grasp axis. (Middle Left) Uncorrelated MAB models maintain an estimate of $P_F$ independently for each grasp, indicated by bars and their height. On iteration $T$ of a MAB algorithm, the evaluated grasp (green bar) is force closure for samples . (Middle Right) Only the estimate of $P_F$ for the sampled grasp is updated on iteration $T+1$, and the grasp with highest estimated $P_F$ remains suboptimal. (Bottom Left) Correlated MAB models maintain a global predictive function (red) of $P_F$ for any possible grasp but may select grasps from a set of discrete candidates (indicated by dots). (Bottom Right) On iteration $T+1$, the evaluated grasp (green dot) is sampl returns force closure and the global model is updated, increasing the estimated $P_F$ for ``nearby" grasps. Although a suboptimal grasp was sampled, the global model now correctly predicts the optimal grasp in the set. }
\figlabel{correlated-motivation}
\vspace*{-15pt}
\end{figure}

@@

A CCBP estimates the shape parameters for a grasp and object $\mY_{i,k} = (\bg_{i,k}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
In this work we use a unit-bandwidth squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} w_m^2 \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_2^2 \right)
\end{align*}
\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space and $w_m \in \mathbb{R}$ are weights scaling the relative contribution of the feature maps to the similarity metric.

Before the first iteration of the MAB algorithm, we update our belief for each candidate grasp to its similarity to all grasps and objects from the database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
%\vspace{-2ex}
\begin{align}
	%p \left(\theta_{i,k} | \mS, \mN \right) &= \betadist\left( \alpha_{i,k,0}, \beta_{j,k,0} \right) \notag \\
	\alpha_{i,k,0} = \alpha_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K k(\mY_{i,k}, \mY_{j,\ell}) S_{j,\ell} \label{eq:alpha-prior} \\
	\beta_{i,k,0} = \beta_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K  k(\mY_{i,k} \mY_{j,\ell}) (N_{j,\ell} - S_{j,\ell}) \label{eq:beta-prior}
\end{align}
\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits}.
% and $\mS$ and $\mN$ are the number of successes and total trials for grasps in the database, respectively.
Upon observing $F_{i,k}$ for grasp $\bg_{i,k}$ on iteration $t$, we update our belief $\theta_{j,k}$ for all other grasps on object $\mO_i$ by~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	\alpha_{j,k,t} &= \alpha_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) F_{i,k} \label{eq:alpha} \\
	\beta_{j,k,t} &= \beta_{j,k,t-1} + k(\mY_{j,k}, \mY_{i,k}) (1 - F_{i,k})\label{eq:beta}
\end{align}

@@

\subsubsection{Grasp Heightmaps}
\secref{local}
We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging}.
Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
Then we assign the heightmap value
\begin{align*}
	\bh_k(u,v) = \minimum{t \geq -r} t \text{ such that } | f\left( \bp_k(u,v) + s_k \bv \right) | < \epsilon
\end{align*}
 where $s_1 = -1$, $s_2 = 1$, $\epsilon$ is the surface threshold used for finding contacts, and $f$ is the SDF of object $\mO$. 
Finally, we make the heightmap rotationally invariant by rotating it to align the axes with the eigenvectors of the weighted covariance matrix of contact points generating the heightmap as described in~\cite{tombariunique}.
Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$. \TODO{This is slightly more complicated but takes a bit to explain; basically the ordering of contacts doesn't matter here}
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty. We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture. Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
\figlabel{global-feature-model}
\vspace*{-15pt}
\end{figure}

\subsection{Optimizing Feature Weights}
One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
%Past work has optimized these weights using a squared error loss on the probability of success predicted by the CCBP and a true probability of success from brute force evaluation~\cite{montesano2012active}.
%However, this criterion may be inappropriate for predicting probabilities, as the predictions must be bounded between 0 and 1.
We select the weights that minimize the cross entropy loss~\cite{}:

\begin{align*}
	w_1^*, ..., w_{N_f}^* = \myargmin{w_1, ..., w_{N_f} \geq 0} \frac{1}{M} \sum \limits_{i=1}^M &\mu_i \log \left( \frac{\alpha_i}{\alpha_i + \beta_i} \right) + \\  &(1 - \mu_i) \log \left( \frac{\beta_i}{\alpha_i + \beta_i} \right)
\end{align*}
\noindent where $\alpha_i$ and $\beta_i$ are the posterior shape parameters given by Equations~\ref{eq:alpha-prior} and~\ref{eq:beta-prior} and $\mu_i$ is the probability of force closure evaluated by exhaustive Monte-Carlo integration for a set of $M$ grasps.
We optimize this objective using SGD with the weights initialized to $w_i = 100$ for all $i$.
\TODO{For experiments so far we actually use a grid search and not SGD but we are interested in using this.}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/correlated_bandits.png}
\caption{(Top Left) Consider a set of grasps with fixed center at an object center of mass and approach direction sampled along a one-dimensional circle. (Top Right) The true probability of force closure $P_F$ as a function of the angle of the grasp axis. (Middle Left) Uncorrelated MAB models maintain an estimate of $P_F$ independently for each grasp, indicated by bars and their height. On iteration $T$ of a MAB algorithm, the evaluated grasp (green bar) is force closure for samples . (Middle Right) Only the estimate of $P_F$ for the sampled grasp is updated on iteration $T+1$, and the grasp with highest estimated $P_F$ remains suboptimal. (Bottom Left) Correlated MAB models maintain a global predictive function (red) of $P_F$ for any possible grasp but may select grasps from a set of discrete candidates (indicated by dots). (Bottom Right) On iteration $T+1$, the evaluated grasp (green dot) is sampl returns force closure and the global model is updated, increasing the estimated $P_F$ for ``nearby" grasps. Although a suboptimal grasp was sampled, the global model now correctly predicts the optimal grasp in the set. }
\figlabel{correlated-motivation}
\vspace*{-15pt}
\end{figure}

@@

A CCBP estimates the shape parameters for a grasp and object $\mY_{i,k} = (\bg_{i,k}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
In this work we use a unit-bandwidth squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{W_m}^2 \right)
\end{align*}
\noindent where $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$ are feature mappings for a grasp and object to a $d_m$-dimensional Euclidean space, $W_m \in \mathbb{R}^{d_m \times d_m}$ are linear transformations scaling the relative contribution of the feature maps to the similarity metric, and $\| \phi \|_{W} = \phi^T W^T W \phi$.

Before the first iteration of the MAB algorithm, we update our belief for each candidate grasp to its similarity to all grasps and objects from the database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
%\vspace{-2ex}
\begin{align}
	%p \left(\theta_{i,k} | \mS, \mN \right) &= \betadist\left( \alpha_{i,k,0}, \beta_{j,k,0} \right) \notag \\
	\alpha_{i,k,0} = \alpha_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K k(\mY_{i,k}, \mY_{j,\ell}) S_{j,\ell} \label{eq:alpha-prior} \\
	\beta_{i,k,0} = \beta_{0} & + \sum \limits_{j=1}^M \sum \limits_{\ell=1}^K  k(\mY_{i,k} \mY_{j,\ell}) (N_{j,\ell} - S_{j,\ell}) \label{eq:beta-prior}
\end{align}
\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits}.
% and $\mS$ and $\mN$ are the number of successes and total trials for grasps in the database, respectively.
Upon observing $F_{i,k}$ for grasp $\bg_{i,k}$ on iteration $t$, we update our belief $\theta_{i, \ell}$ for all other grasps on object $\mO_i$ by~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	\alpha_{i,\ell,t} &= \alpha_{j,\ell,t-1} + k(\mY_{i, \ell}, \mY_{i,k}) F_{i,k} \label{eq:alpha} \\
	\beta_{i,\ell,t} &= \beta_{j,\ell,t-1} + k(\mY_{i,\ell}, \mY_{i,k}) (1 - F_{i,k})\label{eq:beta}
\end{align}

@@

\subsubsection{Grasp Heightmaps}
\secref{local}
We also use a variant of the grasp heightmap features of Herzog et al.~\cite{herzog2012template} and Kappler et al.~\cite{kappler2015leveraging}.
Let $d_h \in \mathbb{Z}$ be the number of pixels along each dimension of the heightmap, let $\mP = \{-d_h, ..., d_h\}$ be the row / column pixel indices for the heightmap, let $\delta \in \mathbb{R}$ be the resolution of the image pixels in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
Then we assign the heightmap value
\begin{align*}
	\bh_k(u,v) = \minimum{t \geq -r} t \text{ such that } | f\left( \bp_k(u,v) + s_k \bv \right) | < \epsilon
\end{align*}
 where $s_1 = -1$, $s_2 = 1$, $\epsilon$ is the surface threshold used for finding contacts, and $f$ is the SDF of object $\mO$. 
Finally, we make the heightmap rotationally invariant by rotating it to align the axes with the eigenvectors of the weighted covariance matrix of contact points generating the heightmap as described in~\cite{tombariunique}.
Our full feature vector for the heightmaps is $\phi_{h}(\bg_i, \mO_i) = [\bh_1, \bh_2]^T$. \TODO{Describe symmetrization of heightmaps for contacts.}
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.

@@

\subsection{Optimizing Feature Weights}
One remaining issue is the selection of the relative feature weights $w_1, ..., w_{N_f}$.
We select the weights that minimize the cross entropy loss~\cite{de2005tutorial}:

\begin{align*}
	w_1^*, ..., w_{N_f}^* = \myargmin{w_1, ..., w_{N_f} \geq 0} \frac{1}{M} \sum \limits_{i=1}^M &\mu_i \log \left( \frac{\alpha_i}{\alpha_i + \beta_i} \right) + \\  &(1 - \mu_i) \log \left( \frac{\beta_i}{\alpha_i + \beta_i} \right)
\end{align*}
\noindent where $\alpha_i$ and $\beta_i$ are the posterior shape parameters given by Equations~\ref{eq:alpha-prior} and~\ref{eq:beta-prior} and $\mu_i$ is the probability of force closure evaluated by exhaustive Monte-Carlo integration for a set of $M$ grasps.
We optimize this objective using SGD with the weights initialized to $w_i = 100$ for all $i$.
\TODO{For experiments so far we actually use a grid search and not SGD but we are interested in using this in final experiments.}

### 2015-09-10 ICRA2016/bandits_docs/includes/conclusion.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\section{Discussion and Future Work}
\seclabel{conclusion}
We introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 20,000 3D object models and a network of similarity between object models and parallel-jaw grasps on each model.
We extended the Multi-Armed Bandit model of Laskey et al.~\cite{laskey2015bandits} to leverage similiarty between grasps based on gripper pose, local surface geometry encoded as heightmaps, and global shape similarity encoded using a state-of-the-art method for shape retrieval based on multi-view Convolutional Neural Networks (CNNs)~\cite{su2015multi}.
Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to select a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature optimization with deep neural networks~\cite{levine2015end} to optimize feature representations of both the local and global surface geometry based on the outcome of grasp evaluations in the bandit algorithms.
We will also study extensions of the shape similarity neural network to predict object class from simulated depth images of objects on a table, which could be useful for transferring learned data from Dex-Net to objects in the physical world.

Another shortcoming is our current use of wrench space metrics, which have been criticized recently for not correlating with human labels~\cite{kappler2015leveraging} or physical trials~\cite{balasubramanian2012physical}.
However, both forms of labels may be difficult to acquire for the entire dataset because of the human and time cost involved.
Future work will research using Multi-Armed Bandits (MABs) to actively acquire grasp evaluations uncertain objects.
To do so, we will study using functional map networks to establish consistent maps between prototypical object parts that indicate grasp affordance, such as handles
We will also build on recent developments in caging to label key the dataset with caging hand configurations either analytically, using simulation, or using a learned model to predict caging configurations.
We will also work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes, integrating Dex-Net with physical robots, and learning statistical models of grasp success using deep learning and MAB.

>>>>

\section{Discussion and Future Work}
\seclabel{conclusion}
We developed a Multi-Armed Bandit algorithm based on correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models, each labelled with up to 250 grasps and the probability of force closure of each.
For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification, trained on milliions of images and thousands of 3D object examples.
Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies using supervision, with the goal of a future system that maps directly from images to motor torques.

Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
This presents a challenge because the number of labels per object and grasp may be smaller thatnwith probability of force closure due to the time cost involved.
Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
We will also add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}.
To achieve this we will work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
